---
title: "Happy Moments"
author: "Arpita Shah and Tian Zheng"
runtime: shiny
---

#A R Notebook Data Story on Happy Moments

## What kind of moments and which ground truth category can influence your happiness

Many things can make one's heart smile with joy. HappyDB is "a corpus of 100,000 crowd-sourced happy moments". 
Participants were given a simple task:

What made you happy today? 

Reflect on the past 24 hours, 
and recall three actual events 
that happened to you that made you happy. 
Write down your happy moment 
in a complete sentence.
(Write three such moments.)

The goal of this project is to look deeper into the causes that make us happy. Natural language processing and text mining are natural tools to derive interesting findings in this collection of happy moments.

In this project we will carry out an exploratory data analysis of the corpus of HappyDB.


```{r load libraries, warning=FALSE, message=FALSE,echo=FALSE}
library(tidyverse)
library(tm)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
library(shiny)
library(igraph)
library(ggraph)
library(tmap)
library(topicmodels)
library(gdalUtils)

```

### Data Structure

We use the processed data (without stopwords) for our analysis and combine it with the demographic information available.

Let's first look at the data structure

```{r load data, warning=FALSE, message=FALSE,echo=FALSE}
hm_data <- read_csv("../output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```


```{r combining data, warning=FALSE, message=FALSE,echo=FALSE}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
summary(hm_data)
```

### EDA (Exploratory Data Analysis)

EDA is for seeing what the data can tell us and the information beyond data. Here, we analyze the dataset to summarize their main characteristics with visual methods.

####The most important part in EDA is the distribution and correlation between each variables and the outliers.

```{r fig.width=8, fig.height=4, warning=FALSE,echo=FALSE}

categoricaldata <- hm_data[which(hm_data$ground_truth_category != "NA"),]

ggplot(hm_data,aes(x = count)) + geom_density()
```

We can see that most of the happy moments are only in a few words.

```{r fig.width=10, fig.height=4, warning=FALSE,echo=FALSE}
ggplot(hm_data,aes(x= gender, y = count)) +  geom_jitter(alpha = 0.1)
```

```{r fig.width=12, fig.height=5, warning=FALSE,echo=FALSE}
ggplot(hm_data,aes(x= country, y = count)) +  geom_jitter(alpha = 0.1) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

From the plots above, we can conclude that there are many outliers and they are highly influenced by different factors.


```{r fig.width=8, fig.height=4, warning=FALSE,echo=FALSE}
ggplot(categoricaldata,aes(x= gender, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)

ggplot(categoricaldata,aes(x= parenthood, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)

ggplot(categoricaldata,aes(x= reflection_period, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)
```

From the above pictures, it is obvious that most the participants can get happy moments from affection and achievement. 
For those married women, they are likely to get happiness from affection than man whose might be more into the exercise and bonding if they are single.
It is interesting that for those single participants with no child, they tend to be happy in their leisure time.
We can also know that participants tends to recalled the same things about their happy moments both in 24 hours and 3 months.


```{r fig.width=12, fig.height=5, warning=FALSE,echo=FALSE}
ggplot(categoricaldata,aes(x= country, y = ground_truth_category, color = parenthood))+ geom_jitter(alpha = 0.4) + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(categoricaldata,aes(x= country, y = ground_truth_category, color = gender))+ geom_jitter(alpha = 0.4) + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(categoricaldata,aes(x= country, y = ground_truth_category, color = reflection_period))+ geom_jitter(alpha = 0.4) + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(categoricaldata,aes(x= country, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

Our participants are mainly come from two countries and it is obvious that people from the USA can get happiness in the same level from each ground truth category.


### Create bag of words and bigrams using the text data

Then we start to look at the top words and the top bigrams

```{r bag of words, warning=FALSE, message=FALSE,echo=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

word_count <- bag_of_words %>%
  count(word, sort = TRUE)
```

```{r bigram, warning=FALSE, message=FALSE,echo=FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)

word_count
bigram_counts
```


### R Shiny app

We want each tab to have its own controls for input and so Shiny's "navbarPage()" layout works the best. We have the first tab visualizing the overall data, second one for scatterplots comparing the proportion of words within categories, third one highlighting the most frequently appearing bigrams based on categories and the last tab to explore the actual happy moments.

```{r shiny UI, warning=FALSE, message=FALSE,echo=FALSE}
ui <- navbarPage("What makes people happy?",
                 tabPanel("Overview",
                          
                          titlePanel(h1("Most Frequent Occurrences",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              sliderInput(inputId = "topWordcloud",
                                          label = "Number of terms for word cloud:",
                                          min = 5,
                                          max = 100,
                                          value = 50),
                              br(),
                              br(),
                              
                              checkboxInput(inputId = "topFreqB",
                                            label = "Plot Bar Chart",
                                            value = F),
                              sliderInput(inputId = "topBarchart",
                                          label = "Number of terms for bar chart:",
                                          min = 1,
                                          max = 25,
                                          value = 10),
                              br(),
                              br(),
                              
                              checkboxInput(inputId = "topFreqN",
                                            label = "Plot Network Graph",
                                            value = F),
                              sliderInput(inputId = "topNetwork",
                                          label = "Number of edges for network graph:",
                                          min = 1,
                                          max = 150,
                                          value = 50)
                            ),
                            
                            mainPanel(
                              wordcloud2Output(outputId = "WC"),
                              plotOutput(outputId = "figure")
                            )
                          )
                 ),
                 
                 tabPanel("Individual Terms",
                          
                          titlePanel(h1("Comparison of Proportions",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              selectInput(inputId = "attribute",
                                          label = "Select the attribute:",
                                          choices = c("Gender" = "gender",
                                                      "Marital Status" = "marital",
                                                      "Parenthood" = "parenthood",
                                                      "Reflection Period" = "reflection_period")
                              )
                            ),
                            
                            mainPanel(
                              plotOutput(outputId = "scatter")
                            )
                          )
                 ),
                 
                 tabPanel("Pair of Words",
                          
                          titlePanel(h1("Most Frequent Bigrams",
                                        align = "center")),
                          
                          sidebarLayout(
                            sidebarPanel(
                              selectInput(inputId = "factor",
                                          label = "Select the attribute:",
                                          choices = c("Gender" = "gender",
                                                      "Marital Status" = "marital",
                                                      "Parenthood" = "parenthood",
                                                      "Reflection Period" = "reflection_period")
                              ),
                              numericInput(inputId = "topBigrams",
                                          label = "Number of top pairs to view:",
                                          min = 1,
                                          max = 25,
                                          value = 10)
                            ),
                            
                            mainPanel(
                              plotOutput(outputId = "bar")
                            )
                          )
                 ),
                 
                 tabPanel("Data",
                          DT::dataTableOutput("table")
                          )
)
```

This shiny app visualizes summary of data and displays the data table itself.

```{r shiny server, warning=FALSE, message=FALSE,echo=FALSE}
server <- function(input, output, session) {
  
  pt1 <- reactive({
    if(!input$topFreqB) return(NULL)
    word_count %>%
      slice(1:input$topBarchart) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      xlab(NULL) +
      ylab("Word Frequency")+
      coord_flip()
  })
  
  pt2 <- reactive({
    if(!input$topFreqN) return(NULL)
    bigram_graph <- bigram_counts %>%
      slice(1:input$topNetwork) %>%
      graph_from_data_frame()
    
    set.seed(123)
    
    x <- grid::arrow(type = "closed", length = unit(.1, "inches"))
    
    ggraph(bigram_graph, layout = "fr") +
      geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                     arrow = x, end_cap = circle(.05, 'inches')) +
      geom_node_point(color = "skyblue", size = 3) +
      geom_node_text(aes(label = name), repel = TRUE) +
      theme_void()
  })
  
  output$WC <- renderWordcloud2({
    
    word_count %>%
      slice(1:input$topWordcloud) %>%
      wordcloud2(size = 0.6,
                 rotateRatio = 0)
    
  })
  
  output$figure <- renderPlot(height = 500, width = 500, {
    
    ptlist <- list(pt1(),pt2())
    ptlist <- ptlist[!sapply(ptlist, is.null)]
    if(length(ptlist)==0) return(NULL)
    
    lay <- rbind(c(1,1),
                 c(2,2))
    
    grid.arrange(grobs = ptlist, layout_matrix = lay)
  })
  
  
  
  selectedAttribute <- reactive({
    list(atr = input$attribute)
  })
  
  output$scatter <- renderPlot({
    temp <- bag_of_words %>%
      count(!!as.name(selectedAttribute()$atr), word) %>%
      group_by(!!as.name(selectedAttribute()$atr)) %>%
      mutate(proportion = n / sum(n)) %>% 
      select(-n) %>% 
      spread(!!as.name(selectedAttribute()$atr), proportion)
    
      ggplot(temp, 
             aes_string(x = colnames(temp)[2], y = colnames(temp)[3]),
             color = abs(colnames(temp)[3] - colnames(temp)[2])) +
      geom_abline(color = "gray40", lty = 2) +
      geom_jitter(alpha = 0.1, size = 1, width = 0.3, height = 0.3) +
      geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
      scale_x_log10(labels = percent_format()) +
      scale_y_log10(labels = percent_format()) +
      scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
      theme(legend.position="none")
  })
  
  
  
  selectedBigram <- reactive({
    list(var = input$factor)
  })
  
  output$bar <- renderPlot({
    hm_bigrams %>%
      count(!!as.name(selectedBigram()$var), bigram, sort = TRUE) %>%
      group_by(!!as.name(selectedBigram()$var)) %>%
      top_n(input$topBigrams) %>%
      ungroup() %>%
      mutate(bigram = reorder(bigram, n)) %>%
      ggplot(aes(bigram, n, fill = !!as.name(selectedBigram()$var))) +
      geom_col(show.legend = FALSE) +
      facet_wrap(as.formula(paste("~", selectedBigram()$var)), ncol = 2, scales = "free") +
      coord_flip()
  })
  
  
  output$table <- DT::renderDataTable({
    DT::datatable(hm_data)
  })
}
```


```{r shiny app, warning=FALSE, message=FALSE,echo=FALSE}
shinyApp(ui, server)
```
