---
title: "Happy Moments"
author: "Arpita Shah and Tian Zheng"
output: html_notebook
runtime: shiny
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

HappyDB is a corpus of 100,000 crowd-sourced happy moments via Amazon's Mechanical Turk. You can read more about it on https://arxiv.org/abs/1801.07746.

Here, we explore this data set and try to answer the question, "What makes people happy?"

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables;
+ `scales` map data to aesthetics, and provide methods for automatically determining breaks and labels for axes and legends;
+ `wordcloud2` provides an HTML5 interface to wordcloud for data visualization;
+ `gridExtra` contains miscellaneous functions for "grid" graphics;
+ `ngram` is for constructing n-grams (“tokenizing”), as well as generating new text based on the n-gram structure of a given text input (“babbling”);
+ `Shiny` is an R package that makes it easy to build interactive web apps straight from R;


```{r load libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)

```

### Step 1 - Load the processed text data along with demographic information on contributors

We use the processed data for our analysis and combine it with the demographic information available.

```{r load data, warning=FALSE, message=FALSE}
hm_data <- read_csv("../output/processed_moments.csv")

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read_csv(urlfile)
```

### Combine both the data sets and keep the required columns for analysis

We select a subset of the data that satisfies specific row conditions.

```{r combining data, warning=FALSE, message=FALSE}
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```

### Create a bag of words using the text data

```{r bag of words, warning=FALSE, message=FALSE}
bag_of_words <-  hm_data %>%
  unnest_tokens(word, text)

word_count <- bag_of_words %>%
  count(word, sort = TRUE)
```

### Create bigrams using the text data

```{r bigram, warning=FALSE, message=FALSE}
hm_bigrams <- hm_data %>%
  filter(count != 1) %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

bigram_counts <- hm_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  count(word1, word2, sort = TRUE)
```
#EDA
```{r, warning=FALSE}
data <- hm_data[which(hm_data$ground_truth_category != "NA"),]

ggplot(data,aes(x = marital, fill = data$ground_truth_category)) + geom_bar(position = "fill")

ggplot(data,aes(x= marital, y = ground_truth_category)) +  geom_jitter(alpha = 0.1)

```

```{r, warning=FALSE}
ggplot(data,aes(x= reflection_period, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)
```

```{r, warning=FALSE}
ggplot(data,aes(x= country, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r, warning=FALSE}
ggplot(data,aes(x= gender, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)

ggplot(data,aes(x= parenthood, y = ground_truth_category, color = marital))+ geom_jitter(alpha = 0.4)
```
